Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-30 reportTII-ArticleHIL.tex
Added to report
I added to the brake subsection in the Modeling Vehicle Subsystems section.

\subsection{Brake System Modeling}

>>>>

\subsection{Brake System Modeling}
To create a brake system model, we first tried generating transfer function models using MATLAB’s System Identification Toolbox. After generating multiple transfer function models and trying many different data log combinations, we still couldn’t find a model that was completely accurate across all combinations and that was below the error bound of 5\% for all combinations. Once this became clear Neural Network models were created using the Neural Network Time Series Toolbox provided by MATLAB to see if they could create accurate brake models. Using this we were able to create a model that accurately tracked the data we collected from the brake system and that stayed within the 5\% error bound.
